---
title: "Quick Analysis"
format: html
---


# Introduction
Data was downloaded from the Arctic Data Center on 10/7/24.
Link to data [here](https://arcticdata.io/catalog/view/doi:10.18739/A25T3FZ8X)

## Set up
Attach necessary packages
```{r}
library(readr)
library(here)
```

## Read data
```{r}
#| message: false
#| warning: false

bg_chem <- read_csv(here("data", "BGchem2008data.csv"))
```


# Analysis
## Calculate summary statistics
```{r explore data}
#| eval: false
#| echo: false

### print the column name
colnames(bg_chem)

str(bg_chem)

## First 6 lines
head(bg_chem)

## summary stat of all columns
summary(bg_chem)

## uniqu values of a column
unique(bg_chem$Date)

```

Calculate the summary statistics for nitrate, ammonia and phosphorate.

```{r}
nitrate <- mean(bg_chem$NO3)
nitrite <- mean(bg_chem$NO2)
amm <- mean(bg_chem$NH4)
phos <- mean(bg_chem$P)

```


## Calculate mean Redfield ratio
This ratio is the relative proportion of nitrogen to phosphorus.

```{r}
ratio <- (nitrate + nitrite + amm)/phos
```

The Redfield ratio for these samples is approximately `r round(ratio)`

## Plot Ratio

```{r}
#| echo: false

plot(bg_chem$P, bg_chem$NO2 + bg_chem$NO3 + bg_chem$NH4)
```


# Conclusion

